Examples Aided Synthesis Examination

### 2020-03-20 abstract.tex
update abstract

\begin{abstract}
Program synthesis has been focusing on making newer and better tools; however,
few have evaluated how people like to interact with them and what features users
find useful.
%
We evaluate the addition of examples to type directed program synthesis.
%
We measured 10 participants between two variants, each with 4 tasks.
%
We do not find a statistical significance, in general, with the addition of
examples.
%
We do note, that one task did have a significant difference in performance
between groups.
%
Further evaluation is needed to determine a reason for this.
\end{abstract}

>>>>

\begin{abstract}
Program synthesis takes the hard work out of \emph{writing} code, at the cost of
having to \emph{read} more code to decipher the best program for a given
situation.
%
This shifts the problem of writing code to reading new, unfamiliar code.
%
We evaluate the addition of examples to type directed program synthesis.
%
We measured 10 participants between two variants, each with 4 tasks.
%
We do not find a statistical significance, in general, with the addition of
examples.
%
We do note, that one task did have a significant difference in performance
between groups.
%
Further evaluation is needed to determine a reason for this.
\end{abstract}
